\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}   % for hyperlinks
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf ROBERT TESTA}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{32 46th Street}
 \moveleft.5\hoffset\centerline{Weehawken, NJ 07086}
 \moveleft.5\hoffset\centerline{(732) 979 - 7722}
 \moveleft.5\hoffset\centerline{RKTesta@gmail.com}

\begin{resume}

\section{SUMMARY}  Decisive Marketing Director who drives company growth through creative and innovative marketing
strategies and sales tactics. Skilled expert on both online and direct marketing campaign stragies, implying a solid 
understanding of digital marketing, including SEO, PPC, SEM and Social Media marketing. 
 
 
\section{SKILLS} {\sl MARKETING \& SALES:} Conducted direct response marketing promotions that boosted business
by 69 percent. Increased patient volume by 144 percent. Raised online engagement and awareness by 285 percent. \\

		{\sl SEO/SEM:} Created and implimented multiple SEO/SEM
		straegies such as landing pages, Google Adwords, and Social Media
		in order to increase online presence. Closely monitor all organic
		and paid traffic to identify areas of performance and oppertunity.\\
         		
         	{\sl MANAGEMENT:} Managed multiple offices cooperatively. 
         	Controlled and prioritized multiple projects simultaneously. 
         	Reduced marketing expenses by 19 percent. \\
 
\section{EXPERIENCE} {\sl Marketing Director} \hfill October 2013 - Current \\
                Bergen Medical Sports \& Spine, Paramus, NJ 
                \begin{itemize}  \itemsep -2pt %reduce space between items
                \item Liaison between 60+ physicians and doctors offices.
                \item Identified, developed and evaluated marketing strategies
                based on knowledge of company objectives and market trends.
                \item Promoted brand awareness with SEO/SEM optimization, 
                attractive web design.
                \end{itemize}
 
                {\sl Marketing Manager} \hfill July 2012 - October 2013 \\
                I T Global Protech, Rochelle Park, NJ
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Created sales strategies to promote advertising offerings and motivate larger sales.
                 \item Initiated and managed all traditional and digital marketing campaigns.
                 \item Made strategic connections with other business's in order to increase sales
                 \end{itemize}
                 
               {\sl Social Media and Marketing Intern} \hfill            May 2012 - June 2013 \\
                SituatioNormal, Montclair, NJ
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developed innovative marketing solutions grounded in clearunderstanding of clients needs.
                 \item Created and managed clients social media accounts, which include Facebook, Twitter,
                 YouTube, and Instagram.
                 \end{itemize} 
 
\section{EDUCATION} {\sl Bachelor of Science,} Marketing \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                Montclair State University, Montclair, NJ, 
                graduated May 2013 \\
\section{ACHIEVEMENTS}
\begin{itemize} 

		\item Montclair State University's 2012 Entrepreneur of the Year
		\item Created \& Studied Abroad in Chile's International Study Program
		\item Completed MSU's CEO Training Program 
					                
					                 
\end{itemize}

\end{resume}
\end{document}




